Review of Edge Detectors

### 2015-04-02 edge-detection-review-3rd-revision-v4.tex
typo

The goal of this work was to provide reference implementations for some of the most classical edge detectors. Some of them have been published for many years and are quite simple, however, it is surprisingly hard to find trustable implementations. We focused on low-level edge detection, which means that we do not consider post processing steps to integrate the detected edgels into meaningul lines.
Extensive qualitative validation has been performed, showing the effects of the parameters and the scale-space properties of the algorithms in order to faithfully compare them.
We consider this work as the first step towards a complete benchmark of edge detectors, which has to be completed with a systemic quantitative analysis. 
Suitable frameworks for this kind of analysis are proposed in the literatura \cite{segm:cardelino:2013:a_contrario_selection_of_optimal_partitions,martin:2001:database_of_human_segmented, cardoso:2005:toward_a_generic_evaluation}, but this is clearly outside the scope of this work.
In particular, quantitatively challenging the claims of the reviewed works will be a great contribution for the area, which is very weak with respect to experimental validation. From the original works reviewed, only Haralick presents a quantitative analysis but only over one synthetic image. Even at the moment of writing (2014), there are only a dozen edge detection and segmentation works presenting a serious quantitative analysis over a standard database of images.

>>>>

The goal of this work was to provide reference implementations for some of the most classical edge detectors. Some of them have been published for many years and are quite simple, however, it is surprisingly hard to find trustable implementations. We focused on low-level edge detection, which means that we do not consider post processing steps to integrate the detected edgels into meaningul lines.
Extensive qualitative validation has been performed, showing the effects of the parameters and the scale-space properties of the algorithms in order to faithfully compare them.
We consider this work as the first step towards a complete benchmark of edge detectors, which has to be completed with a systemic quantitative analysis. 
Suitable frameworks for this kind of analysis are proposed in the literature \cite{segm:cardelino:2013:a_contrario_selection_of_optimal_partitions,martin:2001:database_of_human_segmented, cardoso:2005:toward_a_generic_evaluation}, but this is clearly outside the scope of this work.
In particular, quantitatively challenging the claims of the reviewed works will be a great contribution for the area, which is very weak with respect to experimental validation. From the original works reviewed, only Haralick presents a quantitative analysis but only over one synthetic image. Even at the moment of writing (2014), there are only a dozen edge detection and segmentation works presenting a serious quantitative analysis over a standard database of images.
